% What and how will we model the oceanographic domain, what tools, methods and what kinds of predictions will the models make?

\subsection{Modeling}

A central objective of \proj is to test observational strategies and
evaluate the capacity to characterize and forecast the evolution of
the prevailing coastal ocean conditions using a high resolution
limited area model with assimilation. The expected improvement of this
capacity will reinforce the ability to support different sectors in
the area -- from defense and crisis response operations, to fisheries,
environmental managers and general coastal and nautical
communities. It will also contribute to a significant improvement in
the present understanding of the combined physical and biogeochemical
processes that, in this area, contribute to drive rapid development at
all levels of the trophic chain and shape the coastal ocean
environment and associated ecosystems.  

Central to this effort will be the use of the MIT Multidisciplinary
Simulation, Estimation, and Assimilation System (MSEAS)
\kc{citations?}. The core of the system is a free surface primitive
equation model \kc{Continue MODEL DESCRIPTION MSEAS} integrates a
biogeochemical model developed initially by Dusenberry \kc{citations?}
and latter improved by Lermusiaux \kc{citations?} which integrates 5
compartments (chlorophyll, phytoplankton based on nitrate,
phytoplankton based on ammonia, zooplankton, nitrate, ammonia and
detritus) and 30 parameters.

\proj will provide the opportunity to implement MSEAS at Instituto
Hidrografico (\inste) leveraging work between IH and MIT teams during
the preparatory phase of the exercise \kc{and the \ldots}.

A second and simpler model will also be used during \proje.  The
Harvard Ocean Prediction System (HOPS) is a rigid lid primitive
equations model that integrates an optimal interpolation (OI)
assimilation scheme. HOPS has been used at \inst for the operational
support during Navy exercises, major crises at sea or in the support
of research activities. It has a relatively modest need for
computational resources which are available onboard research
vessels. HOPS is also equipped with the initial version of the
Dusenberry biogeochemical model \kc{citations?}.

The implementation of both these models will be guided by the
experience gathered by a previous implementation of the HOPS model for
the \naz area. The model was configured using a high resolution
Cartesian horizontal grid (300 m resolution), 30 double sigma levels
in the vertical and a realistic topography of the \naz Canyon area
conditioned to meet the hydrostatic consistency requirements.
Atmospheric forcing conditions will be provided by available
operational forecast models. Operational models at \inst use the
analysis and forecasts to 6 days provided by the European Centre for
Medium Range Weather Forecast (ECMWF) and made available by the
Portuguese node at Instituto Portugu\^{e}s do Mar e da Atmosfera (IPMA
-- the Portuguese NOAA).  Boundary conditions at the open boundaries
of the models will be provided by available regional models. These
include the results provided by the Copernicus Marine Service for the
IBIROSS area which are a NEMO model (analysis and forecasts to 5 days,
3km resolution and 50 vertical levels) or the results from the HYCOM
model configuration run operationally at \inst covering the Iberian
area and Moroccan margin.  Boundary conditions at the coastal boundary
associated with freshwater outflows due to some of he small rivers
that directly affect the model domain area will be incorporated using
the information available about discharge conditions provided by the
National Information System on Hydric Resources portal made available
by the Portuguese Agency for the Environment.

\kc{Data sets to model initialization and assimilation \ldots}

\begin{table}[!t]
  \centering
  \vspace{-0.5cm}
  \begin{tabular}{|p{4cm}|p{4cm}|p{4cm}|p{4cm}|}\hline 
    % \rowcolor{Gray}
    \bfseries  &\bfseries Week 1 &\bfseries Week 2 &\bfseries Week 3 \\
    \hline
    Main Goals& Precursor survey; 
                To collect data that allow to build initialization
                fields and define model parameters. To calibrate sensor response (phytoplankton from
                fluorometry, zooplankton from VMADCP)& Update Survey 1:
                                                       AUV operations; potential additional measurements using small boats
                                                       and low cost measurements & Update Survey 2:
                                                                                   Ship measurements during dedicated survey, AUV operations from ship and small boats\\
    \hline
    Observations at sea&&&\\
    \hline
    AUVs&&&\\
    \hline
    Gliders&&&\\
    \hline
    UAVs&&&\\
    \hline
    ASVs&&&\\
    \hline
    Ship-based observations& Ship crossing the area, deploy Multipametric buoy M2
                             CTDs/Water Sampling at key positions
                             VMADCP collected in area/key points&& CTD/LADCP profiles
                                                                   Rosette
                                                                   Samples
                                                                   for
                                                                   nutrients/phyto/zoo-plankton
                                                                   VMADCP on transit and in station. 
                                                                   Daily transmission of  CTD casts and VMADCP data to \inst\\
    \hline
    Small boat operations&CTD + fluorometry + light profiles at key
                           stations. Water samples at key points for
                           nutrients/phyto+zoo-plankton Vertical net
                           samples for phyto+zoo plankton&&\\
    \hline    
    Laboratory Analysis&Samples analyzed for Nutrients at \inst Labs.
                         Samples analyzed for phyto/zoo-plankton&&Post cruise:
                                                                   Samples
                                                                   analyzed
                                                                   for
                                                                   Nutrients
                                                                   at
                                                                   \inst
                                                                   Labs
                                                                   Samples
                                                                   analyzed
                                                                   for
                                                                   phyto/zoo-plankton\\ 
    \hline
    Remote Sensing&SST, Chl, Turbidity images (Sentinel) used to
                    identify the main features and select key points for
                    observation. 
                    Surface fields combined with observations in key
                    points to build initial 3D fields to be used in the
                    models.&SST, Chl, altimetry data used in assimilation
                             Turbidity images used to track impacts (if
                             any) of local rivers and guide
                             observations.&SST, Chl, altimetry data used in assimilation
                                            Turbidity images used to
                                            track impacts (if any) of
                                            local rivers and guide
                                            observations.\\
    \hline
    Models&Build initialization and initial assimilation fields. 
            Start model runs (end of the week).&&\\
    \hline
  \end{tabular}
  \caption{Tasks and activities in \proje.}
  \label{tab:tasks}
\end{table}
