\section{Reporting \& Outreach}

\proj will generate a final report to ONR and ONR Global of the
operations during the course of the field experiment. Detailed
analysis and results from the experiment will be published in
peer-reviewed conferences and journals. Targeted Peer-reviewed
journals including \emph{Science Robotics, J. Field Robotics,
  Int. J. of Robotics Research, AI Journal, Autonomous Robots,
  Oceanography, PLOSone, Frontiers} and high-impact conferences such
as \emph{AAAI, IJCAI, ISER, ICAPS, RSS, IROS, ICRA and IEEE AUV} where
we have published frequently, will be the foci of our efforts.

In addition to Peniche Oceanwatch, \inst has had continued and
extensive engagement over the years with the local authorities
including \naz city officials and local fishermen.  As a result we
will engage the fishing community to carry our low cost
temperature/density sensors and also help provide access to the team
to be able to commute to the islands when necessary, subject to health
protocols. In addition, we expect to engage local high school students
prior and after the experiment, to entice them into thinking about
careers in science and technology, much as we have done in the past
with success in another ONR funded
program~\footnote{\url{https://sunfish.lsts.pt/en/outreach/education}}. 

With the world-wide interest in the \naz area, \proj will also work
with the local authorities and \univ outreach department to showcase
our work in Portuguese and English language media outlets. We will
invite ONR and other ocean science sponsors from the US and government
and private philanthropies to observe the field experiment, in-person
if possible. The PI also expects to involve the US Embassy in outreach
activities \footnote{Rajan is a Fulbright fellow in
  Portugal, Spring 2022 and has extensive connections in the
  country.}. We are also investigating ways in which portions of the
experiment can be livestreamed and made available via Youtube for
general education of non-experts and to entice young researchers into
ocean science and marine robotics. Imagery will be uploaded to
Twitter, Facebook and Instagram as is routine at \ls ~\footnote{See
  \url{https://lsts.pt}} with appropriate context in both the
Portuguese and English.


